Self Referencing Sequences

### 2014-10-26 draft.tex
Edited equivalence
Adding stuff on Reading distance

\section{Equivalence}
\label{equivalence}
\emph{Written by Fermi Ma, edited by Perry Kleinhenz and Erik Waingarten}

@@

\section{An Iterative Process}
\label{iterativeprocess}

>>>>

\section{Equivalence}
\label{equivalence}
\emph{Written by Fermi Ma and Perry Kleinhenz, edited by Erik Waingarten}

@@

We now introduce a notion which will help us categorize sequences as equivalent. 
\begin{definition} Consider a sequence $x$. We say define the read distance for an element $x_i$ as the number of terms in between it and the beginning of the $i$th block of numbers. We denote this as $Rd(x_i)$. 
\end{definition}
The read distance can be any nonnegative integer. For example if we consider the sequence $a_i$ generated by $\{1,2,3\}$ beginning with a 2  
\begin{align*}
2,2,3,3,1,1,1,2,2,2,3,1,2,3,3,1,1,2,2,3,3,3,\dots
\end{align*}
the read distance for the $a_1$ (the first two) is $0$ as the first block of numbers starts at the first number, the read distance for $a_2$ (the second two) is $1$ as the second block of numbers starts at the third number. We can continue to calculate the read distances for this sequence and see that they form a monotonically increasing sequence $0,1,2,4,6,6,6,6,7,8,9,\ldots$. From this we might suspect that the read distance for any self referencing sequence will also be monotonically increasing. We can in fact show a much stronger result. 
\begin{lemma} 
\label{readdistformula}
Let $a_i$ be any self referencing sequence generated by some set of positive integers. Then the read distance for the element $a_i$ for $i>1$ is 
\begin{equation*}
\sum_{k=1}^{i-1}( a_k - 1)
\end{equation*} 
\end{lemma}
\begin{proof}
We will prove this using induction. We know that for $i=1$ the read distance is $0$, as the first block always starts at the first number. For the base case $i=2$ we must show that the read distance is $a_1-1$. Well we know that the first block will be of length $a_1$ since the sequence is self referencing, therefore the second block will begin at \emph{position} $a_1$. The number of elements between position $a_1$ and $2$ is exactly $a_1 -1$.

Now if we assume that our result holds for $i=l$ we would like to show that it holds for $i=l+1$. We know that the distance between the $l$th block and the number at position $l$ is 
\begin{equation*}
\sum_{k=1}^{l-1}( a_k - 1).
\end{equation*} 
This $l$th block has length $a_l$ and so the $l+1$th block will begin $a_l$ positions to the right of the beginning of the $l$th block. Also note that $a_{l+1}$ is one position to the right of $a_l$. Therefore the beginning of the $l+1$th block is 
\begin{equation*}
a_l-1 + \sum_{k=1}^{l-1} (a_k-1) = \sum_{k=1}^{l} (a_k-1)
\end{equation*} 
positions to the right of $a_{l+1}$. But this is exactly the reading distance for $a_{l+1}$ and so we have our result.
\end{proof}
Note that because $a_i$ is generated by positive integers we always have $a_k-1\geq 0$ and the read distance is monotonically increasing. Although this shows us that read distance never decreases it does not tell us how quickly it increases, our next result gives a bound on the number of consecutive times the read distance can stay constant.

\begin{lemma} Consider a self referencing sequence $x$ generated by $\{a_1, a_2, \ldots, a_n\}$ with $a = \max{ a_1, a_2, \ldots, a_n}$. Suppose the read distance for $x_i$ is $d$, then the read distance for $x_{i+a}$ is at least $d+1$. 
\end{lemma}
\begin{proof}
Assume otherwise. By our Lemma ~\ref{readdistformula} we know that the read distance for $x_{i+a}$ is at least $d$. By our assumption it must be exactly $d$. Lemma ~\ref{readdistformula} also tells us that $x_{i+k}=1$ for $k=0,1,2,\ldots, a_n$. But this means that we have a block of length $a+1$, which is a contradiction of the self referencing property of the sequence. Therefore the read distance for $x_{i}$ is at least $d+1$. 
\end{proof}

\begin{theorem} If two sequences are equivalent then the first element of the shared sequence must have the same read distance in both sequences.
\end{theorem}
\begin{proof}
Assume otherwise. So if the two sequences are $a_i$ and $b_i$ and we have 
\begin{equation*}
a_{i+l} = b_{i+k} = c_{i}
\end{equation*}

\end{proof}
\section{An Iterative Process}
\label{iterativeprocess}
